Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-01-31 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor edit
edit for the table of parameters

\author[US]{P. Aram\corref{cor1}}
\ead{p.aram@sheffield.ac.uk}
\author[DEEE,BEI,UE]{D. R. Freestone}
\ead{dfreestone@bionicear.org} 
\author[UE,CU]{M. Dewar}
\ead{mike.dewar@columbia.edu}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt}
\author[DEEE,BEI]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & \parham{synaptic time constant} \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & backward posterior state estimates & mV\\
	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
	$P^b_t$ & backward posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\ 
	$\mathcal S_{t} $ & smoother gain & n.a.\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}
\doublespacing

@@

\begin{align}\label{eq:Xi0derivation0} 
 \mathbf M_{t+1}&=\mathbf E_{\theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1})^\top\right] \nonumber \\
&=\mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\mathbf x_t\hat{\mathbf x}_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\mathbf x_{t+1}^\top\right]+\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\right]  \nonumber \\
&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top+\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\nonumber \\
&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top.
\end{align}
Rearranging  equation \eqref{eq:Xi0derivation0} we get
\begin{equation}\label{eq:Xi0derivation1}
 \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
\end{equation}
substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum we get
\begin{equation}
 \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
\end{equation}   
An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by expanding the covariance matrix,
\begin{equation}\label{eq:appXi1}
 \boldsymbol\Xi_1=\mathbf E_{\theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t}\mathbf x_{t}^\top\right],
\end{equation}
therefore we can write
\begin{equation}\label{eq:Xi1derivation1}
 \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
\end{equation}
substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
\begin{equation}
 \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
\end{equation}

\bibliographystyle{./elsarticle/model2-names} 
\bibliography{MRAIDE}

>>>>

\author[US]{P. Aram\corref{cor1}}
\ead{parham.aram@univ-amu.fr}
\author[DEEE,BEI,UE]{D. R. Freestone}
\ead{dfreestone@bionicear.org} 
\author[UE,CU]{M. Dewar}
\ead{mike.dewar@columbia.edu}
\author[UM]{K. Scerri}
\ead{kenneth.scerri@um.edu.mt}
\author[DEEE,BEI]{D. B. Grayden}
\ead{grayden@unimelb.edu.au}
\author[US]{V. Kadirkamanathan}
\ead{visakan@sheffield.ac.uk}

@@

\section{IDE Neural Field Model}
\singlespacing
\begin{table*}[!t]
\begin{tabular}{|l|l|l|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Units}\\
	\hline
	\multicolumn{3}{|c|}{\emph{Domain and indices}}\\
	\hline
	$\Omega$ & spatial domain & n.a.\\
	$\mathbf{r}$ & spatial location & [mm, mm]\\
	$t$ & time & s\\
	\hline
	\multicolumn{3}{|c|}{\emph{Model}}\\
	\hline
    $y_t$ & observation & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & mV \\
	$f(v\left(\mathbf{r},t\right))$ & firing rate function & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, with covariance function $\eta(\mathbf r-\mathbf r')$ & mV\\
	$\boldsymbol\varepsilon_t$ & observation noise, with covariance matrix $\Sigma_\varepsilon$ & mV\\
	$m(\mathbf{r}_n)$ & observation kernel where $n$ is sensor index $n=1,..,n_y$ & n.a. \\
	$w(\mathbf{r})$ & spatial connectivity kernel & n.a.\\
	$h(t)$ & post-synaptic response kernel & mV\\
	$\tau$, $\xi$ & membrane time constant \& time constant parameter & s, n.a.\\
	$\delta(t)$ & Dirac-delta function & n.a.\\
	\hline
	\multicolumn{3}{|c|}{\emph{Reduced Model}} \\
	\hline
   	$\mathbf{x}_t$ & state vector at time $t$ & mV\\
   	$\mathbf{e}_t$ & state disturbance vector, with covariance $\Sigma_e$ & mV\\
   	$\mathbf{C}$ & observation matrix & n.a. \\
	\hline
	\multicolumn{3}{|c|}{\emph{Frequency Analysis}} \\
	\hline
	$\boldsymbol{\nu}$, $\boldsymbol{\nu}_c$ & spatial frequency and spatial cutoff frequency & cycles/mm \\
	$\sigma_{\nu}^2$ & variance of Fourier transformed Gaussian basis function & (cycles/mm)$^2$\\
	\hline
	\multicolumn{3}{|c|}{\emph{Estimation}} \\
	\hline
	$\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^f$ & forward prior and posterior state estimates & mV\\
	$\hat{\mathbf{x}}_t^{b}$ & backward posterior state estimates & mV\\
	$P^{f-}_t$, $P^f_t$  & forward prior and posterior covariance matrices & mV$^2$\\
	$P^b_t$ & backward posterior covariance matrices & mV$^2$\\
	$M_t$& cross-covariance matrix & mV$^2$\\
	$\mathcal K_{t} $ & filter gain & n.a.\\ 
	$\mathcal S_{t} $ & smoother gain & n.a.\\
	\hline
\end{tabular}
\caption{\textbf{Notation.} The first column of the table gives the symbols for all the notation used in the paper. The second column provides a brief description of the quantity, and the third column provides the SI units where relevant.}
\label{tab:Notation}
\end{table*}  
\doublespacing

@@

\begin{align}\label{eq:Xi0derivation0} 
 \mathbf M_{t+1}&=\mathbf E_{\theta'}\left[(\mathbf x_t-\mathbf{\hat x}_t)(\mathbf x_{t+1}-\mathbf{\hat x}_{t+1})^\top\right] \nonumber \\
&=\mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\mathbf x_t\hat{\mathbf x}_{t+1}^\top\right]-\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\mathbf x_{t+1}^\top\right]+\mathbf E_{\theta'}\left[\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\right]  \nonumber \\
&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top+\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top\nonumber \\
&= \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]-\hat{\mathbf x}_t\hat{\mathbf x}_{t+1}^\top.
\end{align}
Rearranging  equation \eqref{eq:Xi0derivation0} we get
\begin{equation}\label{eq:Xi0derivation1}
 \mathbf E_{\theta'}\left[\mathbf x_t\mathbf x_{t+1}^\top\right]=\mathbf M_{t+1}+\mathbf {\hat x}_t\mathbf{\hat x}_{t+1}^\top
\end{equation}
substituting \ref{eq:Xi0derivation1} into \ref{eq:appXi0}, noting the expectation commutes with the sum we get
\begin{equation}
 \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf M_{t+1}+\mathbf{\hat x}_t\mathbf{\hat x}_{t+1}^\top\right)
\end{equation}   
An expression for $\boldsymbol\Xi_1$ in terms of the smoothed states can be also found in a similar way by expanding the covariance matrix,
\begin{equation}\label{eq:appXi1}
 \boldsymbol\Xi_1=\mathbf E_{\theta'}\left[\sum_{t=0}^{T-1}\mathbf x_{t}\mathbf x_{t}^\top\right],
\end{equation}
therefore we can write
\begin{equation}\label{eq:Xi1derivation1}
 \mathbf E_{\theta'}\left[\mathbf x_{t}\mathbf x_{t}^\top\right]=\mathbf P_{t}+\mathbf {\hat x}_{t}\mathbf{\hat x}_{t}^\top,
\end{equation}
substituting \ref{eq:Xi1derivation1} into \ref{eq:appXi1} we get
\begin{equation}
 \boldsymbol\Xi_1=\sum_{t=0}^{T-1}\left(\mathbf P_{t}+\mathbf{\hat x}_{t}\mathbf{\hat x}_{t}^\top\right).
\end{equation}
\newpage
\bibliographystyle{./elsarticle/model2-names} 
\bibliography{MRAIDE}
